### 2021-05-14 LaTeX-ACM/sections/paper.tex
front running is a mess still

Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology. This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity. Such a design appears feasible but is considered too slow. Together, we agreed it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and in practice) providing future efficiency gains for on-chain trading, (2) demand for on-chain trading is exemplified by the recent popularity of dealer quote-based trading like Uniswap and Curve Finance (reviewed below), and (3) stablecoins have become popular and allow on-chain trading with pricing in USD, alleviating another regulatory hook: the need for platforms to maintain traditional accounts for holding governmental currency and interfacing with the banking system.

@@

%\textblue{Notes on Front-running Table:}
%\begin{itemize}
%\item{Mallory squeezes her order before Alice's.} Mallory sees that there is an incoming bid at 200 for 10 of an asset, and currently, the best offer is at 190 for the same volume. In this case, Mallory sends her bid at 190 for 10 and immediately inserts the sell order at 200. If Alice's transaction gets executed, Mallory will profit on the price difference. 
%\textblue{Sandwich Attacks:} These attacks apply to automated market makers (\ie UniSwap) and exploit a particular feature of AMMs, which is for every swap that takes place on an AMM, the price of the token being swapped shifts slightly. In this case, if Mallory realizes that there is an incoming trade of asset A for asset B, She immediately inserts a bid for asset B. This transaction will increase the price of asset B significantly and when Alice's transaction gets executed on the AMM, she'll receive less number of asset B as she is purchasing it at an inflated price. Right after Alice's transaction goes through, Mallory will sell the amount of asset B she has bought at a higher price.
%\end{itemize}
\input{tables/frontrunning.tex}

The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcast.

@@

Potential for front-running still exists around ties on price and order cancellations (both discussed in the next section). Finally, \textit{displacement attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added. Both are expensive attacks. For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = =  %
\subsection{Front-running on Arbitrum}

>>>>

% JC: Our research group is actively collaborating with our jurisdiction's (Quebec, Canada) financial regulator, the Autorité des Marchés Financiers (AMF), to help them forecast how trading can be impacted by blockchain technology.

Our research group is actively collaborating with our jurisdiction's financial regulator (name withheld for anonymity) to help them forecast how trading can be impacted by blockchain technology. This paper addresses their concerns about the feasibility of a `worst-case scenario' where a trading platform is anonymously deployed on a public blockchain, like Ethereum, and runs autonomously without any further intervention from an externally visible entity. Such a design appears feasible but is considered too slow. Together, we agreed it is a very good time to do a deep dive into understanding precisely \textit{how slow} for the following reasons: (1) public blockchains are becoming faster (both in theory and in practice) providing future efficiency gains for on-chain trading, (2) demand for on-chain trading is exemplified by the recent popularity of dealer quote-based trading like Uniswap and Curve Finance (reviewed below), and (3) stablecoins have become popular and allow on-chain trading with pricing in USD, alleviating another regulatory hook: the need for platforms to maintain traditional accounts for holding governmental currency and interfacing with the banking system.

@@

%\textblue{Notes on Front-running Table:}
%\begin{itemize}
%\item{Mallory squeezes her order before Alice's.} Mallory sees that there is an incoming bid at 200 for 10 of an asset, and currently, the best offer is at 190 for the same volume. In this case, Mallory sends her bid at 190 for 10 and immediately inserts the sell order at 200. If Alice's transaction gets executed, Mallory will profit on the price difference. 
%\textblue{Sandwich Attacks:} These attacks apply to automated market makers (\ie UniSwap) and exploit a particular feature of AMMs, which is for every swap that takes place on an AMM, the price of the token being swapped shifts slightly. In this case, if Mallory realizes that there is an incoming trade of asset A for asset B, She immediately inserts a bid for asset B. This transaction will increase the price of asset B significantly and when Alice's transaction gets executed on the AMM, she'll receive less number of asset B as she is purchasing it at an inflated price. Right after Alice's transaction goes through, Mallory will sell the amount of asset B she has bought at a higher price.
%\end{itemize}

\input{tables/frontrunning.tex}

As we illustrate in Table~\ref{tab:front}, call markets have a unique profile of resilience against \emph{front-running attacks}~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash} that differs somewhat from continuous-time markets and automated market makers. Traders are sometimes distinguished as \emph{makers} (adds orders to a market) and \emph{takers} (trades against a pre-existing, unexecuted orders). A continuous market has both. All traders with an automated market maker are takers, while the investors who provide tokens (or liquidity) to the AMM for trading are makers. Under our definition, a call market only has makers: the only way to have a trade executed is to submit an order. The front-running attacks in Table~\ref{tab:front} are sub-categorized, using a recent SoK~\cite{eskandari2019sok}, as being \emph{Insertion}, \emph{Displacement}, and \emph{Suppression}. To illustrate the difference, we will consider the first three attacks in the table.

 fronting attacks: 
t

(i) in an \emph{displacement attack}, Mallory knows of a transaction from Alice and inserts her transaction before Alice's and does not care what happens to Alice's transaction; (ii) in an \emph{insertion attack}, Mallory similarly inserts a transaction before Alice and ensures Alice's transaction is the next to run, and (iii) in a \emph{suppression attack}, Mallory displaces all future transactions for some period of time. Mallory can be a miner which can freely order transactions within the blocks it creates, or Mallory can be a fast user (or bot) who can quickly react to Alice's broadcasted but unconfirmed transactions, likely offering higher gas fees to have her transactions prioritized over Alice's. Later in Section~\ref{sec:frontarb}, we discuss a third kind of participant: sequencers.

Consider the first two attacks in Table~\ref{tab:front}. Talk about our cattegories from front-running paper.

 Call markets are less vulnerable to these basic insertion and displacement attacks because they do not have any time priority (e.g., if you were to shuffle the order of all orders submitted within a window of time to a call market, the outcome would be exactly the same). A different way to mitigate these attacks is to add confidentiality on the orders (cite Tex, Hisham) which

 A, and the same sequence is randomly shuffled and submitted to market B. In a call market, the outcome of A and B will be exactly equivalent, which is not true in the other types.The remove of time priority

 There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcast.

@@

Potential for front-running still exists around ties on price and order cancellations (both discussed in the next section). Finally, \textit{supression attacks}~\cite{eskandari2019sok} are possible where competitive orders are delayed long enough for the market to close without them or the adversary fills up the current market (which caps the number of orders) to ensure other orders cannot be added. Both are expensive attacks. For all these reasons, we say \cm reduces front-running attacks but stop short of saying this issue is completely solved by \cm.

@@

% = = = = = = = = = = = = = = = = = = = = = = = = =  %
\subsection{Front-running on Arbitrum}
\label{sec:frontarb}
